---
title: "FRAPPE-AOA"
author: "William Cooper"
date: "12/18/2014"
output: html_document
---


\newcommand{\datetoday}{\number\day\space
     \ifcase\month\or January\or February\or March\or April\or May\or
     June\or July\or August\or September\or October\or November\or
     December\fi
     \space\number\year}
The speed run from 15:50:00 to 15:55:00 on FRAPPE flight 4 provides
good data for determining the angle-of-attack sensitivity coefficients. The basic 
equation that provides a reference for calibration is:

$$ \alpha_{\mathrm{ref}}=\theta-\frac{W_p}{V}=b_0+b_1\frac{\Delta p}{q} $$

where $\theta$=PITCH, $W_p$=GGVSPD, $V$=TASX, $\Delta p$=ADIFR, and $q$=QCF. 
The choice for representing q is based on QCF
being more reliable than QCR and not requiring prior pressure-defect
correction as does PSXC (the use of which introduces circularity in the
calculation because the pressure correction itself depends on angle of
attack). The left equality of (1) relies on the vertical wind being
zero, so the use of this result depends on the calibration maneuver
being flown in air without vertical motion.
```{r, echo=FALSE,include=FALSE}
require(knitr)
thisFileName <- "FRAPPE-AOA"
require(Ranadu, quietly = TRUE, warn.conflicts=FALSE)
require(ggplot2)
require(grid)
require(ggthemes)

```


```{r,echo=TRUE,include=TRUE}
Flight <- "rf04"        
Project = "FRAPPE"
fname = sprintf("%s%s/%s%s.nc", DataDirectory (), Project, Project, Flight)
VarNames <- c("TASX", "ADIFR", "PITCH", "QCF", "GGVSPDB")
Data <- getNetCDF (fname, VarNames, Start=155000, End=155500)
if (!"GGVSPD" %in% names(Data)) {
  Data$GGVSPD <- Data$GGVSPDB
}
attach(Data)

Data$AOAREF <- PITCH - asin(GGVSPD/TASX) *180 / pi
Data$AQR <- ADIFR / QCF # basic pressure ratio for AOA
```


```{r,echo=TRUE,include=TRUE, fig.cap="Fit AOA vs reference AOA  from Eq. 1. The orange dashed line shows the fit for which details and coefficients are shown in the text."}

fmy <- lm (AOAREF ~ AQR, data=Data)
print (summary (fmy))
cfr <- coefficients (fmy)
A1 <- cfr[1] + cfr[2] * Data$AQR
#plot (AOAREF, A1, pch=16, cex=0.8, col='blue', xlab="Ref. AOA", ylab="fit AOA")
#lines (c(-3.,6.), c(-3.,6.), lty=2, lwd=3, col='darkorange')
detach (Data)
g <- ggplot (data=Data, aes (x=AOAREF, y=AQR))
g <- g + geom_point (pch=20, col='blue')
g <- g + geom_smooth (method='lm', col='darkorange', lty=2, lwd=1.5)
g <- g + xlab ("Reference AOA [deg.]") + ylab ("AOA from fit [deg.]") + theme_WAC()
print (g)

```

The best-fit coefficients obtained by fitting (1) to the speed-run data are $b_0$ = `r cfr[1] ` and $b_1$ = `r cfr[2]`. The residual standard error is `r round(summary(fmy)$sigma, 2)` and the square of the correlation coefficient is `r round(summary(fmy)$r.squared, 3)`, so the fit is very good.

\begin{center}
\textsf{\textcolor{blue}{-- End of Memo --\vfill\eject}}
\par\end{center}

__Reproducibility:__

\begin{tabular}{ll}
\textsf{\textsc{\textcolor{blue}{Project:}}} & `r thisFileName`\tabularnewline
\textsf{\textsc{\textcolor{blue}{Archive package:}}} & `r thisFileName`.zip\tabularnewline
\textsf{\textsc{\textcolor{blue}{Contains:}}} & attachment list below\tabularnewline
\textsf{\textsc{\textcolor{blue}{Program:}}}  & `r thisFileName`.Rmd\tabularnewline
\textsf{\textsc{\textcolor{blue}{Original Data:}}} &  /home/data/FRAPPE/FRAPPErf04.nc\tabularnewline   
\textsf{\textsc{\textcolor{blue}{Git:}}} &  git@github.com:WilliamCooper/`r Project`.git\tabularnewline
\end{tabular}

\noindent __Attachments:__    
\   `r thisFileName`.Rmd  
\   `r thisFileName`.pdf  
\   `r thisFileName`.Rdata  
\   SessionInfo

```{r,echo=FALSE}
MQCF <- system(sprintf("ncdump -h %s%s/%s%s.nc | grep 'QCF:Cal'", DataDirectory(), Project, Project, Flight), intern=TRUE)
MADIFR <- system(sprintf("ncdump -h %s%s/%s%s.nc | grep 'ADIFR:Cal'", DataDirectory(), Project, Project, Flight), intern=TRUE)
```



\noindent __Some relevant cal coefficients:__  
\   `r MQCF`  
\   `r MADIFR`  
```{r,echo=FALSE}
cat (toLatex(sessionInfo()), file="SessionInfo")
save (Data, file=sprintf("./%s.Rdata", thisFileName))

```

```{r, echo=FALSE}

system (sprintf("zip %s.zip %s.Rnw %s.pdf %s.Rdata SessionInfo", thisFileName, thisFileName, thisFileName, thisFileName))
```


